Portfolio prioritization of salmon conservation

### 2013-05-01 inst/examples/salmonport.Rmd
Bankruptcy commit

```{r env-ts, fig.height=4, fig.width=4, cache = FALSE, fig.cap="Example temperature time series\\label{fig:env-ts}"}
#library(metafolio)
#or for rapid development:
library(devtools)
metafolio_files <-  list.files(path = "../../R/")
for(i in 1:length(metafolio_files)){
   source(paste("../..//R/", metafolio_files[i], sep = ""));rm(i)}
#load_all("../../") # Not working with knitr?
source("plot_env_ts.R")
col_pal <- rev(gg_color_hue(10))
```

>>>>

```{r env-ts, fig.height=4, fig.width=4, cache = FALSE, fig.cap="Example temperature time series\\label{fig:env-ts}"}

library(devtools)

RELOAD_R_PACKAGE <- FALSE

if(RELOAD_R_PACKAGE) {
  document("../../")
  build("../../")
  if("metafolio" %in% loaded_packages()) 
    detach("package:metafolio", unload = TRUE)
  install.packages("~/Dropbox/ms/metafolio_0.1.tar.gz", type = "source", repos = NULL, INSTALL_opts = "--byte-compile")
  library(metafolio)
}

metafolio_files <-  list.files(path = "../../R/")
for(i in 1:length(metafolio_files)){
   source(paste("../..//R/", metafolio_files[i], sep = ""));rm(i)}

#load_all("../../")

source("plot_env_ts.R")
col_pal <- rev(gg_color_hue(10))
```
